Global well-being and mental health in the internet age

### 2023-05-23 ms.Rmd
Edit figures for presentation

p1 <- itu %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile,
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 150, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  ) %>% 
  bind_rows(gwp) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value (%)",
    # Display percentages
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = interaction(country, outcome)
    ),
    size = .05, col = "dodgerblue3"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none"
  )

x <- fits_wb %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>%   
  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
  scale_color_brewer(
    "Association", palette = "Set2", aesthetics = c("fill", "color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks()
  ) +
  stat_halfeye(
    aes(shape = after_stat(sign(xmax) == sign(xmin))),
    position = position_dodge(.15), 
    normalize = "xy", 
    height = .8,
    point_interval = "mean_qi",
    fatten_point = 3,
    point_fill = "white",
    size = .25,
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
    ) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.x = element_line(
      color = "black", linetype = "dotted", size = .1
    )
  )

(p1 / p2) + 
  plot_layout(heights = c(8, 2)) +
  plot_annotation(tag_levels = "A")
```

@@

```{r fig-gwp-country}
#| cache: false
figure_country <- function(data) {
  data %>% 
    # Show countries and main relations
    filter(factor == "r_country") %>% 
    drop_na(Predictor) %>% 
    # Take out countries with only time association from this figure
    add_count(outcome, country) %>% 
    filter(n > 1) %>% 
    # Arrange per panel
    group_by(Predictor, outcome) %>% 
    arrange(Predictor, outcome, Mean) %>% 
    mutate(y = 1:n()) %>% 
    ggplot(aes(Mean, y, col = cred)) +
    scale_color_manual(values = c("dodgerblue1", "dodgerblue3")) +
    scale_y_discrete(
      "Country",
      # Fix country names
      labels = ~str_replace_all(., "\\.", " ") %>% 
        str_replace_all(., "’", "'"),
      expand = expansion(.015)
    ) +
    scale_x_continuous(
      "Estimated linear association",
      breaks = extended_breaks(6), 
      expand = expansion(c(0.01))
    ) +
    scale_shape_manual(values = c(21, 19)) +
    scale_linetype_manual(values = c(1, 1, 1)) +
    geom_linerangeh(
      size = .1,
      aes(xmin = CI_low, xmax = CI_high, linetype = cred)
    ) +
    geom_point(
      aes(shape = cred), 
      size = .55, fill = "white", stroke = .2
    ) +
    guides(
      linetype = "none", 
      shape = "none",
      color = guide_legend(override.aes = list(size = .5, stroke = 1))
    ) +
    facet_grid2(
      Predictor~outcome,
      scales = "free",
      independent = "all",
      labeller = labeller(
        .cols = as_labeller(~str_replace(., "_", " "))
      )
    ) +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      panel.grid.major.x = element_line(
        color = "black", linetype = "dotted", size = .1
      ),
      legend.position = "none"
    )
}
p_country_wb <- figure_country(tab_wb)
```

>>>>

p1 <- itu %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile,
  ) %>%
  # Truncate mobile percentages for figure
  mutate(
    Mobile = if_else(Mobile > 150, NaN, Mobile),
    ) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  ) %>% 
  bind_rows(gwp) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
  filter(region != "Oceania", year >= 2005) %>% 
  filter(outcome %in% c("Internet", "Mobile", "Life_satisfaction")) %>% 
  mutate(year = make_date(year)) %>%
  mutate(country = fct_relevel(country, "Netherlands") %>% fct_rev()) %>%
  ggplot(
    aes(
      year, 
      mean, 
      size = country == "Netherlands", 
      color = region == "Europe"
    )
  ) +
  scale_size_manual(values = c(0.25, 0.25)) +
  scale_color_manual(values = c("white", "white")) +
  scale_y_continuous(
    "Value (%)",
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = interaction(country, outcome)
    )
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    text = element_text(size = 18), 
    panel.spacing = unit(10, "pt"),
    axis.title.x = element_blank(),
    legend.position = "none"
  )
p1
x <- fits_wb %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>% 
  filter(outcome == "Life_satisfaction") %>% 
  filter(Predictor != "Time") %>% 
  ggplot(aes(value, fct_rev(Predictor), fill = x, color = x)) +
  scale_color_manual(
    "Association", 
    values = c("#fc8d62", "#66c2a5"), 
    aesthetics = c("fill", "color", "interval_color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks()
  ) +
  scale_y_discrete(
    expand = expansion(c(0.001, .01)),
    drop = FALSE
  ) +
  stat_slabinterval(
    aes(shape = after_stat(sign(xmax) == sign(xmin))),
    position = position_dodge(-.1),
    normalize = "xy", 
    height = .9,
    point_interval = "mean_qi",
    interval_size_range = c(.25, 1),
    fatten_point = 4,
    point_fill = "white",
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
  ) +
  geom_vline(xintercept = 0, linewidth = .25) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  guides(shape = "none") +
  theme(
    legend.position = "bottom",
    axis.title.y = element_blank(),
    text = element_text(size = 18), 
    panel.spacing = unit(10, "pt")
  )
p2
```

@@

```{r fig-gwp-country}
#| cache: false
figure_country <- function(data) {
  data %>% 
    # Show countries and main relations
    filter(factor == "r_country") %>% 
    drop_na(Predictor) %>% 
    # Take out countries with only time association from this figure
    add_count(outcome, country) %>% 
    filter(n > 1) %>% 
    # Arrange per panel
    group_by(Predictor, outcome) %>% 
    arrange(Predictor, outcome, Mean) %>% 
    mutate(y = 1:n()) %>% 
    ggplot(aes(Mean, y, col = cred)) +
    scale_color_manual(values = c("dodgerblue1", "dodgerblue3")) +
    scale_y_discrete(
      "Country",
      # Fix country names
      labels = ~str_replace_all(., "\\.", " ") %>% 
        str_replace_all(., "’", "'"),
      expand = expansion(.015)
    ) +
    scale_x_continuous(
      "Estimated linear association",
      breaks = extended_breaks(6), 
      expand = expansion(c(0.01))
    ) +
    scale_shape_manual(values = c(21, 19)) +
    scale_linetype_manual(values = c(1, 1, 1)) +
    geom_linerangeh(
      size = .3,
      aes(xmin = CI_low, xmax = CI_high, linetype = cred)
    ) +
    geom_point(
      aes(shape = cred), 
      size = 1, fill = "white", stroke = .3
    ) +
    guides(
      linetype = "none", 
      shape = "none",
      color = guide_legend(override.aes = list(size = .5, stroke = 1))
    ) +
    facet_grid2(
      Predictor~outcome,
      scales = "free",
      independent = "all",
      labeller = labeller(
        .cols = as_labeller(~str_replace(., "_", " "))
      )
    ) +
    theme(
      text = element_text(size = 18), 
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      panel.grid.major.x = element_line(
        color = "black", linetype = "dotted", size = .1
      ),
      legend.position = "none"
    )
}
p_country_wb <- figure_country(tab_wb %>% filter(outcome == "Life_satisfaction"))
p_country_wb
```
